MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-04 paper/paper.tex
clarity change left behind

Mel-Frequency Cepstral Coefficients, or MFCCs, are a widely used feature set for speech recognition and other audio processing applications. They are a competitive feature set because they mimic what the human ear perceives \cite{9996362}.

>>>>

Mel-Frequency Cepstral Coefficients, or MFCCs, are a widely used feature set for speech recognition and other audio processing applications. They are a competitive feature set because they mimic what the human ear perceives \cite{9996362}. The process of extracting MFCCs involves several steps that convert raw audio into a compact representation of its spectral characteristics. One of the key stages in this process is the de-correlation of the log energies from a filter bank. The following quote provides a more detailed explanation of how MFCC coefficients are derived:
